\artus{} -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-10-27 Core/doc/latex/include/bib.tex
Paper: Further changes after discussion
Paper: More references

 \begin{thebibliography}{99}

    \bibitem{joram_phd}Joram Berger,
      \textit{Search for the Higgs Boson Produced via Vector-Boson
                        Fusion in the Decay Channel H $\to \tau \tau$},
      CERN-THESIS-2014-092.

\end{thebibliography}

>>>>

 \begin{thebibliography}{99}
    \bibitem{joram_phd}Joram Berger,
      \textit{Search for the Higgs Boson Produced via Vector-Boson
                        Fusion in the Decay Channel H $\to \tau \tau$},
      \href{https://cds.cern.ch/record/1747055}{\texttt{CERN-THESIS-2014-092}}.
    \bibitem{cmssw}\url{https://github.com/cms-sw/cmssw}
    \bibitem{root}
      Rene Brun and Fons Rademakers, 
      \emph{ROOT -- An Object Oriented Data Analysis Framework}, 
      Proceedings AIHENP'96 Workshop, Lausanne, Sep. 1996, Nucl. Inst. \& Meth. in Phys. Res. A \textbf{389} (1997) 81--86. See also \url{http://root.cern.ch}.
    \bibitem{cms}
      CMS Collaboration,
      \emph{The CMS Experiment at the CERN LHC},
      JINST \textbf{3} (2008) S08004, 
      \textsc{doi}: \href{http://dx.doi.org/10.1088/1748-0221/3/08/S08004}{\texttt{10.1088/1748-0221/3/08/S08004}},
    \bibitem{wlcg}
      \url{http://wlcg-public.web.cern.ch}.
\end{thebibliography}

### 2015-10-27 Core/doc/latex/paper.tex
Paper: More references

Following the structure of the CMSSW~\cite{cmssw} \todo[inline]{Referenz? zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
The complete structure is explained in the next section~\ref{section_artus_structure}.

>>>>

Following the structure of the CMSSW~\cite{cmssw} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
The complete structure is explained in the next section~\ref{section_artus_structure}.
